### 2016-05-16 text/new_formal_background.tex
Initial version of disambiguated matching in formal notation.

@@

A typed graph homomorphism between $g$ and $g'$ is a function $f: f_v \cup f_e$ such that:
\begin{itemize}
\item $f_v: V\rightarrow V'$
\item $f_e: E\rightarrow E'$
\item $\forall v_1 \xrightarrow{e} v_2\in E$:
\begin{itemize}
\item $f_v(v_1), f_v(v_2) \in V'$
\item $f_e(e) \in E'$
\item $s'(f_e(e)) = f_v(v_1)$, $t'(f_e(e)) = f_v(v_2)$
\item $\mathit{matchesOver}(\tau(v_1), \tau(f_v(v_1)) \land \\\mathit{matchesOver}(\tau(v_2), \tau(f_v(v_2)) \land\\ \mathit{matchesOver}(\tau(e), \tau(f_e(e))$
\end{itemize}

@@

@@

\paragraph{\textbf{Notation:}}
\bentley{Try to cut this as much as possible}
In order to simplify our notation, when the context is unambiguous we will abbreviate a typed graph $\langle V,E,st,\\\tau,\VT, \ET\rangle$ as as 4-tuple $\langle V,E,st,\tau\rangle$. Also, given a typed graph $g\in \textsc{Tg}$, will use the notation $Components(g)$ to describe the set of strongly connected typed graphs in $g$. Finally, we will use the notation $g|_{t}$ to refer to the restriction of graph $g$ to its subgraph containing only edges of type $t$.

>>>>

Given a typed graph $g\in \textsc{Tg}$, will use the notation $Components(g)$ to describe the set of strongly connected typed graphs in $g$. Also, we will use the notation $g|_{t}$ to refer to the restriction of graph $g$ to its subgraph containing only edges of type $t$.

@@

A typed graph homomorphism between $g$ and $g'$ is a function $f: f_v \cup f_e$ such that:
\begin{itemize}
\item $f_v: V\rightarrow V'$
\item $f_e: E\rightarrow E'$
\item $\forall v_1 \xrightarrow{e} v_2\in E$:
\begin{itemize}
\item Let $ v_1' = f_v(v_1), v_2' = f_v(v_2), e' = f_e(e)$
\item $v_1', v_2' \in V', e' \in E'$
\item $s'(e') = v_1'$, $t'(e') = v_2'$
\item $\mathit{matchesOver}(\tau(v_1), \tau(v_1') \land \\\mathit{matchesOver}(\tau(v_2), \tau(v_2') \land\\ \mathit{matchesOver}(\tau(e), \tau(e')$
\end{itemize}

@@

\subsubsection*{Typed Graph Edge Homomorphism}

Our technique also requires a form of graph homomorphism that primarily focuses on matching the edges of the graphs. This homomorphism will be an injective match regarding the edges, but note that a particular vertex in the source graph may match onto multiple vertices in the target graph. \bentley{What's the term for this?}

\begin{definition}{Typed Graph Edge Homomorphism\\}
\label{def:typed_graph_edge_homomorphism}
\defineggprime

A typed graph edge homomorphism between $g$ and $g'$ is a function $h: h_v \cup h_e$ such that:
\begin{itemize}
\item $h_v: V'\rightarrow V$
\begin{itemize}
\item Note that $h_v$ is an function from a vertex in the target graph onto a vertex in the source graph
\end{itemize}
\item $h_e: E\rightarrow E'$
\item $\forall v_1 \xrightarrow{e} v_2\in E$:
\begin{itemize}
\item Let $e' = h_e(e), v_1' = s'(e'), v_2' = t'(e')$
\item $v_1', v_2' \in V', e' \in E'$
\item $v_1 = h_v(v_1'), v_2 = h_v(v_2')$
\item $\mathit{matchesOver}(\tau(v_1), \tau(v_1') \land \\\mathit{matchesOver}(\tau(v_2), \tau(v_2') \land\\ \mathit{matchesOver}(\tau(e), \tau(e')$
\end{itemize}

\end{itemize}  
\end{definition}

Again, we wish to highlight the fact that this homomorphism is different than Definition~\ref{def:typed_graph_homomorphism} in the vertex matching function. A vertex in the target graph matches onto a vertex in the source graph, with multiple target vertices matching onto the same source vertex. 
\bentley{Create diagram to illustrate}

This unusual homomorphism allows our technique to `split' our source graph over multiple locations in the target graph. This is critical, as our target graphs are constructed in a way that allows for vertex duplication. That is, two vertices of a particular type in the target graph may only represent one underlying element, as discussed in Section~\ref{sec:abstraction_relation}. Constructing this morphism allows our prover implementation to avoid explicitly creating `disambiguated' graphs where these duplications are resolved.

@@
